Framing Effects in the Wild: How the News Media Shapes Public Opinion by Defining Political Issues

### 2022-07-08 paper/Manuscript_Framing.Rmd
add renv

---
title: "Framing Effects in the Wild: How the News Media Shapes Public Opinion by Defining Political Issues"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    includes:
      in_header: preamble.tex
subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
fontsize: 12pt
geometry: margin=1.5in
abstract: "A vast body of research is devoted to the persuasive effects of news framing. However, the study of the effects of framing has almost exclusively taken an experimental approach, with limited external validity. I provide the first real-world study of framing effects by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing. Combining panel data from over 15,000 individuals with content analysis of 2.5 million newspaper articles using transformer models and a difference-in-differences design, I show that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, nor did it increase the association of migration attitudes with attitudes about crime. These findings fundamentally challenge the generalizability of framing effects research and add to a recent body of empirical studies questioning the role of the news media for opinion formation in the twentyfirst century."
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
---

@@

The persuasiveness of the news media has been a fixation of research on political communication and public opinion for at least the past 100 years. One of the largest fields within this literature is concerned with framing effects. A huge body of experimental evidence suggests that citizens substantially alter their issue attitudes when presented with different frames [@Busby2019; @Chong2007b; @Leeper2020; @Nelson1997Rally; @sniderman2004structure; @Slothuus2008a]. However, there is little research investigating whether these findings translate into a messy reality [@Barabas2010], where frames are communicated by specific actors, and citizens self-select into media outlets, potentially shielding them from some frames and exposing them to others.

>>>>

---
title: "Framing Effects in the Wild: How the News Media Shapes Public Opinion by Defining Political Issues"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    includes:
      in_header: preamble.tex
subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
fontsize: 12pt
geometry: margin=1.5in
abstract: "A vast body of research is devoted to the persuasive effects of news framing. However, the study of the effects of framing has almost exclusively taken an experimental approach, with limited external validity. I provide the first observational estimate of framing effects by exploiting a unique case from Germany, where an editorial change in Germany's largest tabloid - *Bild* - led to a substantial shift in the paper's migration framing. Combining panel data from over 15,000 individuals with content analysis of 2.5 million newspaper articles using transformer models and a difference-in-differences design, I show that a substantial increase in the emphasis of crime in migration coverage did not affect immigration attitudes, nor did it increase the association of migration attitudes with attitudes about crime. These findings fundamentally challenge the generalizability of framing effects research and question worries about the news media|s power to shape public opinion."
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
---

@@

The persuasiveness of the news media has been a fixation of research on political communication and public opinion for at least the past 100 years. One of the largest fields within this literature is concerned with framing effects. A huge body of experimental evidence suggests that citizens substantially alter their issue attitudes when presented with different frames [@Busby2019; @Chong2007b; @Leeper2020; @Nelson1996; @Nelson1997Rally; @sniderman2004structure; @Slothuus2008a]. However, there is little research investigating whether these findings translate into a messy reality [@Barabas2010], where frames are communicated by specific actors, and citizens self-select into media outlets, potentially shielding them from some frames and exposing them to others.
